---
title: "DeepLearningML"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DeepLearningML}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{R}
library(DeepLearningML)
```

### 1. Train a Deep Learning Model

You can train a deep learning model using your metabolomics dataset. 
For example, let's create a small dataset and train a model:

```{r train_dl_model}
library(h2o)
h2o.init()
data <- data.frame(
  x1 = rnorm(100),
  x2 = rnorm(100),
  y = sample(0:1, 100, replace = TRUE)
)
model <- train_dl_model(data, target = "y", epochs = 10)
h2o.shutdown(prompt = FALSE)
```

### 2. Train Machine Learning Models

The package supports multiple machine learning algorithms 
like RF, SVM, RPART, and more using the `caret` package. 
Here is how you can train a set of machine learning models:

```{r train_ml_models, eval=FALSE, warning=FALSE}
library(caret)
# train machine learning models
ml_models <- train_ml_models(data, target = "y")
# access the trained Random Forest model
rf_model <- ml_models$rf
```

### 3. Evaluate Models

After training models, you can evaluate their performance 
using AUC and ROC curves. Here's how to do it:

```{r evaluate_models, eval=FALSE}
results <- evaluate_models(ml_models, data, target = "y")
print(results)
```

### 4. Feature Importance

You can assess the importance of features in the trained models 
using the `feature_importance()` function:

```{r feature_importance}
# calculate feature importance for the Random Forest model
importance <- feature_importance(rf_model)
print(importance)
```

## Available Functions

### `train_dl_model()`

- **Description**: Trains a deep learning model using the `h2o` package.
- **Parameters**:
  - `data`: A data frame containing input features and the target variable.
  - `target`: The name of the target variable (output).
  - `epochs`: The number of epochs to train the model (default: 50).
- **Returns**: A trained H2O deep learning model.

### `train_ml_models()`

- **Description**: Trains a set of machine learning models using the `caret` package.
- **Parameters**:
  - `data`: A data frame containing input features and the target variable.
  - `target`: The name of the target variable (output).
- **Returns**: A list of trained models.

### `evaluate_models()`

- **Description**: Evaluates the performance of trained models using ROC curves and AUC.
- **Parameters**:
  - `models`: A list of trained models.
  - `data`: A data frame containing test data.
  - `target`: The name of the target variable.
- **Returns**: A vector of AUC values for each model.

### `cross_entropy()`

- **Description**: Computes the cross-entropy loss between true labels and predicted labels.
- **Parameters**:
  - `x`: True labels.
  - `z`: Predicted labels.
- **Returns**: The cross-entropy loss.

### `feature_importance()`

- **Description**: Computes the importance of features in a trained machine learning model.
- **Parameters**:
  - `model`: A trained machine learning model from `caret` or `h2o`.
- **Returns**: A data frame of feature importance scores.
